### 2017-04-27 paper/jfp-submission/locating.tex
prune orphans
update location numbers

For each pair of an ill-typed program and its fix, we run \toolname and
collect two sets of source locations:
%
(1) the source location corresponding to the stuck term; and
%
(2) the source locations that \emph{produced} the values inside the
stuck term.
%
For example, in the @sqsum@ program from \S~\ref{sec:advantage-traces}
the stuck term is \verb!0 @ 1!.
%
This corresponds to the call to \verb!@! on line 3, and contains
the literal @0@ from line 2 and the value @1@ produced by the
@*@ on line 3.

@@

We evaluate each tool based on whether \emph{any} of its predictions
identifies a changed expression.
%
There were a number of student programs where \mycroft or \sherrloc
encountered an unsupported language feature or timed out after one
minute, or where \toolname failed to produce a witness.
%
We discard all such programs in our evaluation to level the playing
field, leaving us with a benchmark set of 1,612 programs.

\begin{figure}[t]
\includegraphics[width=0.8\linewidth]{blame.png}
\caption{Accuracy of type error localization. \toolname's witness-based
  predictions outperform \ocaml by 20 points, and are competitive
  with the state-of-the-art tools \mycroft and \sherrloc.}
\label{fig:results-blame}
\end{figure}

>>>>

For each pair of an ill-typed program and its fix, we run \toolname and
collect two sets of source locations:
%
(1) the source location corresponding to the stuck term; and
%
(2) the source locations that \emph{produced} the values inside the
stuck term.
%
Intuitively, these two classes of locations correspond to \emph{sinks}
and \emph{sources} for typing constraints.
%
For example, in the @sqsum@ program from \S~\ref{sec:advantage-traces}
the stuck term is \verb!0 @ 1!.
%
This corresponds to the call to \verb!@! on line 3, and contains
the literal @0@ from line 2 and the value @1@ produced by the
@*@ on line 3.

@@

We evaluate each tool based on whether \emph{any} of its predictions
identifies a changed expression.
%
There were a number of student programs where \mycroft or \sherrloc
encountered an unsupported language feature or timed out after one
minute, or where \toolname failed to produce a witness.
%
We discard all such programs in our evaluation to level the playing
field, leaving us with a benchmark set of 1,569 programs.

\begin{figure}[t]
\includegraphics[width=0.8\linewidth]{blame.png}
\caption{Accuracy of type error localization. \toolname's witness-based
  predictions outperform \ocaml by 22 points, and are competitive
  with the state-of-the-art tools \mycroft and \sherrloc.}
\label{fig:results-blame}
\end{figure}
